\documentclass[12pt,a4paper,leqno]{report}

\usepackage[ansinew]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsthm}
\usepackage{amsfonts}         
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{chemformula}
\usepackage{siunitx}



\pagestyle{plain}
\setcounter{page}{1}
\addtolength{\hoffset}{-1.15cm}
\addtolength{\textwidth}{2.3cm}
\addtolength{\voffset}{0.45cm}
\addtolength{\textheight}{-0.9cm}

\title{Iron samples with XAS}
\author{Antti-Jussi Kallio}
\date{}

\begin{document}

\maketitle

\tableofcontents

\chapter{Introduction}\label{johd}



\chapter{Phosphorus and Iron Cycling in the Aquatic System }\label{phosphorus}
The Baltic Sea and the water area in front of Finland is greatly affected by soil erosion and aquatic eutrophication. The agriculture in the coastal nations plays a key role in the soil-originating \ch{P} load in aquatic system.  

\section{Soil as a Carrier of \ch{Fe} and \ch{P}}

\section{\ch{Fe} Cycling in Sediment and Fate of \ch{P}}

\section{The Effects of \ch{C}/\ch{Fe} Ratio}

\chapter{X-ray Absorption Spectroscopy}\label{XAS}
X-ray absorption spectroscopy focuses on studying how x-rays are absorbed above and below the element specific jumps in the absorption cross-section called absorption edges. 
\section{X-ray Absorption and Fluorescence}
\section{Theoretical Description of XAS}
\section{Transmission and Fluorescence}

\chapter{Measurement setup}\label{setup}
\section{Setup}
\subsection{Monochromators}
\subsection{Preparations for Anaerobic Samples}


\chapter{Sample Preparation}\label{preparation}
\section{Reference Samples}\label{ref}
\section{Samples}\label{samples}
\subsection{Soil Samples}
\subsection{Slurries}
\subsection{Anaerobic Slurries}


\chapter{Results and Analysis}\label{tulokset}
\section{Analysis}
\subsection{Data Reduction}
\subsection{Data Modelling}
\section{Measurement results}
\subsection{Soil Samples}
\subsection{Slurries}
\subsection{Anaerobic Slurries}

\chapter{Conclusion}\label{conc}



\begin{thebibliography}{9}

\bibitem{Soil erosion}
Petri Ekholm, Jouni Lehtoranta.
\textit{Does control of soil erosion inhibit aquatic eutrophication}.
Journal of Environmental Management 93 (2012) 140-146.

\bibitem{Labile carbon}
Lehtoranta J., Ekholm P., Wahlström S., Tallberg P., Uusitalo R.
\textit{Labile organic carbon regulates phosphorus release from eroded soil transported into anaerobic coastal system}.
Ambio 2015, 44(Suppl. 2) 263-273.

\bibitem{Ros}
Jilbert T., Asmala E., Schröder C., Tiihonen R., Myllykangas J-P., Virtasalo J. J., Kotilainen A., Peltola P., Ekholm P., Hietanen S.
\textit{Impacts of flocculation on the distribution and diagenesis of iron in boreal estuarine sediments}.
Biogeosciences 15 (2018) 1243-1271. 

\bibitem{Tuo}
Pekka Tuominen: Todennäköisyyslaskenta I, 5.\ painos, Limes ry, 2000.

\end{thebibliography}

\end{document}
